Strict Pure Functional Programming and Automatic Parallelization\\ (Project-in-progess Paper)

### 2016-02-17 pubs/tfp16/paper.tex
synching

@@

C stack, our stack.

>>>>

Proper tail calling is achieved.  Because we maintain our own data and control
(continuation) stack all generated C functions take no arguments and have return
type void, and with a single exception are invoked in tail call position, both
gcc and Clang/LLVM generate jumps instead of calls.  The exception is a convenience.
As described in the fast curry paper we have a generic stgApply function that
is used for applications of non-known functions, and known functions with
a deficit or excess number of arguments.  The stgApply function takes as arguments
the object (FUN, PAP, or THUNK) and its arguments, and if a THUNK, evaluates it
with a call (rather than jump) to yield a FUN or PAP.  This allows us to implement
a single stgApply function...can we split this?

@@
